---
title: "frequency modulated tone"
author: "Brian C Leavell"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Generating frequency modulated tone for use in ultrasonic microphone calibration

Goal: Generate broad-spectrum, frequency modulated tone as .wav file.

Why?: Why not? ...To be used for calibration of WildLife Acoustics microphone and Song Meter acoustic recording unit sensitivities.

```{r packages}
library(tuneR)
library(seewave)
```

Create file

Settings:
90 - 1 kHz frequency sweep
Sine wave
Fade-in & Fade-out = 10 msec
Sample rate = 192 kHz
Bit depth = 16 (PCM)
Duration = 2 seconds

```{r tone}
fmtone <- synth(f = 192000,
                cf = 90000,
                d = 2,
                a = 1,
                signal = "sine",
                fm = c(0,0,-89000,0,0),
                output = "Wave"
                )

fmtone <- fadew(fmtone, din = 0.010, dout = 0.010, shape = "exp", output = "Wave") # 10 msec fade in and fade out
savewav(fmtone, filename = "90to1kHz_fmtone.wav") #final file save as .wav
```

## Oscillogram
``` {r oscillo}
oscillo(fmtone)
```

## Power spectrum
``` {r powerspec}
meanspec(fmtone,  wl = 256)
```

## Spectrogram
``` {r spectrogram}
spectro(fmtone,  wl = 1024)
```
