---
title: "white noise generation"
author: "Brian C Leavell"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Generating white noise for use in ultrasonic microphone calibration

Goal: Generate broad-spectrum, ultrasonic white noise .wav file.

Why?: Why not? ...To be used for calibration of WildLife Acoustics microphone and Song Meter acoustic recording unit sensitivities.

```{r packages}
library(tuneR)
library(seewave)
```

Create white noise file

Settings:
Butterworth band-pass filter (1-90 kHz pass)
Fade-in & Fade-out = 10 msec
Sample rate = 192 kHz
Bit depth = 16 (PCM)
Duration = 2 seconds

```{r noise}
whitenoise <- noise(kind = "white",
                    samp.rate = 192000,
                    bit = 16,
                    pcm = TRUE,
                    duration = 2, 
                    xunit = "time") #xunit time defaults to seconds

# oscillo(whitenoise) #oscillogram of unedited white noise
# meanspec(whitenoise,  wl = 1024) #spectrogram of unedited white noise
writeWave(whitenoise, filename = "ultrasound_white_noise.wav") #unfiltered/unedited .wav

filtered_whitenoise <- bwfilter(whitenoise, n = 5, from = 1000, to = 90000, bandpass = TRUE, output = "Wave") # band-pass filter
filtered_whitenoise <- fadew(filtered_whitenoise, din = 0.010, dout = 0.010, shape = "exp", output = "Wave") # 10 msec fade in and fade out

savewav(filtered_whitenoise, filename = "1to90kHz_bandpass_ultrasound_white_noise.wav") #final file save as .wav
```

## Oscillogram
``` {r oscillo}
oscillo(filtered_whitenoise)
```

## Power spectrum
``` {r powerspec}
meanspec(filtered_whitenoise,  wl = 256)
```

